Datasheet for 'A dataset

### 2024-03-14 paper/datasheet.qmd
Update and rename

---
title: "Datasheet for 'A dataset'"
author: 
  - Yang Zhou
  - Yuean Wang
  - Dong Jun Yoon
thanks: "Code and data are available at: <https://github.com/yangzhoucoco/Political-support-in-the-United-States.git.>"
date: "`09 March 2024`"
date-format: "09 March 2024"
abstract: "The CES 2022 dataset, collected through an online survey by YouGov, encompasses 60,000 instances representing U.S. adult citizens' electoral behaviors, political opinions, and demographic characteristics. The instances are detailed and categorized by election experiences, contextual data, demographic information (e.g., gender, race, education), political affiliations, and opinions on various policy issues. The dataset employs a matched random sampling methodology, with its representativeness validated through a two-stage weighting process involving entropy balancing and iterative proportional fitting. Preprocessing included sample matching, weighting, and vote validation, ensuring data quality and representativenes in order to avoid representative bias."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Datasheet for 'A dataset'"
author: 
  - Dong Jun Yoon
  - Yuean Wang
  - Yang Zhou
thanks: "Code and data are available at: <https://github.com/yangzhoucoco/Political-support-in-the-United-States.git.>"
date: "`09 March 2024`"
date-format: "09 March 2024"
abstract: "The CES 2022 dataset, collected through an online survey by YouGov, encompasses 60,000 instances representing U.S. adult citizens' electoral behaviors, political opinions, and demographic characteristics. The instances are detailed and categorized by election experiences, contextual data, demographic information (e.g., gender, race, education), political affiliations, and opinions on various policy issues. The dataset employs a matched random sampling methodology, with its representativeness validated through a two-stage weighting process involving entropy balancing and iterative proportional fitting. Preprocessing included sample matching, weighting, and vote validation, ensuring data quality and representativenes in order to avoid representative bias."
format: pdf
number-sections: true
bibliography: references.bib
---
